%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experiences}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Dept. of Computer Science, Korea Military Academy} % Organization
{Lecturer \& Assistant Professor} % Job title
{Jun. 2015 -  Present} % Date(s)
{Seoul, S.Korea} % Location
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Assistant Professor. Sep. 2016 - Present}
\item {Lecturer. Jun. 2015 - Sep. 2016}
\item {Server administrator officer. Jan. 2017 - Present}
\item {Administrative officer. Jan. 2016 - Dec. 2016}
\item {Courses in charge: Introduction to Computer Science, Computer Programming (Java, Python), Introduction to Cyber Warfare}
\item {Developed a web service (Code Evaluation System) which evaluates submitted code automatically.}
\item {Participated in a research project which suggests adoption of IPv6 in military network of Korea.}
\item {Managed capstone project which suggests utilizing k-means algorithm to SNS analysis.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Data Intensive Computing Lab (DICL), UNIST} % Organization
{Research Assistant \& Teaching Assistant} % Job title
{Mar. 2013 - Feb. 2015} % Date(s)
{Ulsan, S.Korea} % Location
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Courses in charge as TA: Engineering Programming(C++), Computer Architecture}
\item {Implemented and managed code submission\&evaluation program. (Written in C++ language with Bash script)}
\item {Implemented a prototype of MapReduce framework (EclipseMR) which utilizes semantic memory cache.}
\item {Developed a job shceduling middleware which leverages EM-KDE algorithm.}
\item {Conducted a research to apply data migration in a distributed cache infrastructure.}
\item {Configured and managed server cluster which has 40 CentOS nodes.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Dept. of Computer Science, University of Maryland} % Organization
{UROP (Undergraduate Research Opportunities Program)} % Job title
{Jun. 2011 - Sep. 2011} % Date(s)
{College Park, Maryland, US} % Location
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Developed a cache-aware job scheduling algorithm named DEMB.}
\item {Worked as visiting intern student with Prof. Alan Sussman.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{LG Electronics} % Organization
{LG Electronics Internship Program} % Job title
{Jan. 2012 - Feb. 2012} % Date(s)
{Changwon, S.Korea} % Location
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Tested smartphone app for electronic appliances.}
\item {Investigated proper wireless communication for electronic appliances.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Data Intensive Computing Lab (DICL), UNIST} % Organization
{Undergraduate Research Assistant \& Undergraduate Teaching Assistant} % Job title
{Oct. 2010 - Feb. 2013} % Date(s)
{Ulsan, S.Korea} % Location
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Devised a job scheduling algorithm DEMB during the UROP program.}
\item {Implemented a Java Swing program which visualizes the connetivity of nodes inside a peer-to-peer grid system.}
\item {Courses in charge as TA: Engineering Programming(C++)}
\end{cvitems} 
}

%------------------------------------------------

\end{cventries}
