%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Projects}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{A web service which evaluates submitted code automatically} % Brief explanation
{Code Evaluation System} % Project name
{Korea Military Academy} % Location
{Jan. 2016 - Jun. 2018} % Date(s)
{ % Description(s)
\begin{cvitems}
\item {The system manages database of courses, students, assignments and submissions
via PostgreSQL. It automatically \newline compiles submitted code and compares output
of the code to correct output, and gives scores. Supported languages are Python 2/3, Java.}
\item {The web service is served with Django and Nginx on RHEL. Back-end processing is mostly implemented in Python.
Techniques used in front-end side include Javascript, JQuery, CSS, LESS, Ajax etc.
The whole stacks(front-end/back-end) are implemented from scratch.}
\item {Using this system, students could get feedbacks right after the submissions in real time.
And professors could save a lot of time to evaluate and grade all the submissions.}
\item {The system is maintained successfully for two semesters in two courses(Java, Python).}
\item {Github link: https://github.com/youngmoon01/CES}
\end{cvitems}
}

%------------------------------------------------

\cventry
{A capstone design project conducted with students in Korea Military Academy} % Brief explanation
{Capstone Design Project} % Project name
{Korea Military Academy} % Location
{Jan. 2017 - Dec. 2017} % Date(s)
{ % Description(s)
\begin{cvitems}
\item {Keyword extraction based on TF-IDF algorithm.}
\item {Suggested document grouping of SNS documents with k-means clustering.}
\item {Implemented a crawler to crawl documents from Facebook pages.}
\item {Written in Python 3 with facebook-sdk, NLTK (Natural Language Toolkit).}
\item {Succesfully clustered documents by k-means clustring algorithm and extracted important words.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{A research project to suggests IPv6 adoption model to military network of Korea} % Brief explanation
{IPv6 Adoption Model in Military Network of ROK} % Project name
{Korea Military Academy} % Location
{Jan. 2017 - Jun. 2017} % Date(s)
{ % Description(s)
\begin{cvitems}
\item {Investigated progress of international/domestic IPv6 adoption both in military
area and industrial area.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{A prototype of MapReduce framework like Hadoop, Spark, etc} % Brief explanation
{EclipseMR, a MapReduce framework employing semantic caches} % Project name
{UNIST} % Location
{Jan. 2014 - Present} % Date(s)
{ % Description(s)
\begin{cvitems}
\item {A MapReduce framework which works on two layers of storage, distributed in-memory
caches and DHT file system.}
\item {Locality-aware fair job scheduling policy is implemented as a task scheduler.}
\item {Could get better performance than Apache Hadoop, Apache Spark from some usual
MapReduce applications such as Wordcount, PageRank, k-means clustering etc.}
\item {The program is mainly written in C++ from scratch. Technical challenges such as socket
programming, multi-process/multi-task programming, Inter-Process Communication were involved
in this project.}
\item {Github link: https://github.com/DICL/Eclipse}
\end{cvitems}
}

%------------------------------------------------

\cventry
{A project to design job scheduling policies in distributed environments} % Brief explanation
{Job Scheduling Policy for Multi-dimensional Data Processing} % Project name
{UNIST} % Location
{Dec. 2010 - Jun. 2015} % Date(s)
{ % Description(s)
\begin{cvitems}
\item {The Hilbert space-filling curve was implemented and used over this projects
to convert multi-dimensional problem space into \newline one-dimensional space.}
\item {Suggested DEMB which records past queries and divide problem space according to the record.}
\item {Improved the DEMB algorithm and devised EM-KDE which uses exponentially moving kernel density
estimation.}
\item {Developed data migration policy for distributed cache infrastructure.}
\item {Suggested collaborative scheduling in the use case of geographically distributed
cloud systems.}
\item {Algorithm implementation and evaluations of each scheduling algorithm were conducted
with an event-driven simulator written \newline in Java.}
\end{cvitems}
}

%------------------------------------------------

\end{cventries}
