%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Publications}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Vicente A. B. Sanchez, Wonbae Kim, Youngmoon Eom, Kibeom Jin, Moohyeon Nam, Deukyeon Hwang, Jik-Soo Kim, and Beomseok Nam} % Authors
{EclipseMR: Distributed and Parallel Task Processing with Consistent Hashing} % Title
{} % No Location
{Sep. 2017} % Date(s)
{ % No description(s)
\begin{cvitems}
\item {19th IEEE International Conference on Cluster Computing}
\item {The first three authors contributed equally in this work.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Youngmoon Eom, Jonghwan Moon, Deukyeon Hwang, Junyong Lee, Minho Shin, and Beomseok Nam} % Authors
{EM-KDE: A Locality-Aware Job Scheduling Policy with Distributed Semantic Caches} % Title
{} % No Location
{Sep. 2015} % Date(s)
{ % No description(s)
\begin{cvitems}
\item {Journal of Parallel and Distributed Computing (JPDC) Volume 83}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Youngmoon Eom, Jinwoong Kim, and Beomseok Nam} % Authors
{Multi-dimensional Multiple Query Scheduling with Distributed Semantic Caching Framework} % Title
{} % No Location
{Sep. 2015} % Date(s)
{ % No description(s)
\begin{cvitems}
\item {Cluster Computing, Vol. 18, No. 3, Springer 2015}
\end{cvitems}
}

%------------------------------------------------
\cventry
{Youngmoon Eom, Jinwoong Kim, Deukyeon Hwang, Jaewon Kwak, Minho Shin, Beomseok Nam} % Authors
{Improving Multi-dimensional Query Processing with Data Migration in Distributed Cache Infrastructure} % Title
{} % No Location
{Dec. 2014} % Date(s)
{ % No description(s)
\begin{cvitems}
\item {The 21st annual IEEE International Conference on High Performance Computing}
\end{cvitems}
}

%------------------------------------------------
\cventry
{Youngmoon Eom, Jonghwan Moon, Jinwoong Kim, and Beomseok Nam} % Authors
{Collaborative Multi-dimensional Dataset Processing with Distributed Cache Infrastructure in the Cloud} % Title
{} % No Location
{Sep. 2014} % Date(s)
{ % No description(s)
\begin{cvitems}
\item {2nd International Workshop on Autonomic Management of Grid and Cloud Computing (in conjunction with ACM CAC 2014)}
\end{cvitems}
}

%------------------------------------------------
\cventry
{Junyong Lee, Youngmoon Eom, and Beomseok Nam} % Authors
{DEMB: Cache-Aware Scheduling for Distributed Query Processing} % Title
{} % No Location
{May. 2012} % Date(s)
{ % No description(s)
\begin{cvitems}
\item {16th Workshop on Job Scheduling Strategies for Parallel Processing (JSSPP 2012), in conjunction with IPDPS 2012}
\end{cvitems}
}

%------------------------------------------------

\end{cventries}
